Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-12-04 parts/morph.tex
CLEAN UP code, removing comments
working on report/letter2
editors corrections

The main input of a modeller to the process is a markup of the
candidate lens system, which we call a spaghetti diagram.  This is a
sketch of the arrival-time surface from a point-like source, with
proposed locations of maxima, minima and saddle points, and an implied
time-ordering of the images.  Such information encodes a starting
proposal for the mass distribution.  A spaghetti diagram is thus a
completely abstract construction, and moreover it refers to a
simplified system with a point source.  However, spaghetti diagrams
are intuitive because they tend to resemble the form of lensed arcs
\citep[see Fig.3 of][]{2008MNRAS.383..857F}, and of course they are
simple to draw, and easy to vary and refine in an open collaborative
environment. This makes them very practical for non-professional lens
enthusiasts in the citizen-science community.  Details and tests are
given in \citet{2015MNRAS.447.2170K}.

We now discuss the diagnostics that can be taken from the process of
drawing the spaghetti diagram, even before detailed mass-modelling
takes place.  Fig.~\ref{fig:splinput} shows nine examples, each
consisting of a cutout of the \SW  image of a lens candidate,
marked up with a spaghetti diagram.
The volunteers are initially presented a square image with side
82\arcsec (440~pixels) in full size, but they have the
ability to zoom in individually.
The cutouts presented in Figs.~\ref{fig:splinput} to \ref{fig:kappa}
are rescaled during post-processing, relative to the outermost image.
% it's a factor L/(L-4) with L=pixradius, for L=12 -> 1.5
% maprad = rmax * L / (L-4)

@@

The third diagnostic tests whether the lens is isolated, or whether
other galaxies could contribute to the lensing.  For this, we do not
consider stars or other clearly foregound objects.  Additional
galaxies contributing to the lensing mass can be marked by the
volunteer alongside the spaghetti diagrams.  An example can be seen as
the grey dot and circle in the cutout with \sw{57} at the top right of
Fig.~\ref{fig:splinput}.  Objects marked in this way are modelled as
point masses.  Other possible contributors to lensing are galaxies or
groups that are not in the immediate vicinity of the lensed images,
yet massive enough to exert an influence. These are accounted for by
allowing a constant but adjustable external shear.

We remark that the lack of expected lensed images, or the presence of
blended images or perturbing galaxies do not imply that a given
candidate is unlikely to be a lens.  This means, rather, that the
models are more uncertain and perhaps could be more easily improved by
trying further variations in the markup.

The fourth diagnostic is based on the fact that the arrangement of
lensed images of a pointlike source through a non-circular
gravitational lens depends on the location of the source relative to
the long and short axes of the lens.  This dependence is quite robust
and independent of many other details of the lensing mass
distribution.  Sources close to being dead-centre behind a lens tend
to produce quads; sources at larger transverse distance tend to
produce doubles.  We denote these as Q and D, respectively, and add a
prefix to the Q systems, as follows: we write LQ if the source is
inferred as displaced along the long axis of the lens, SQ if displaced
along the short axis, IQ if inclined to both axes, CQ if only very little or
no displacement is evident.  Although the
unlensed source and its location are obviously not seen, the LQ, SQ, IQ and CQ
cases correspond to easily-seen image morphologies \citep[see,
  e.g.,][]{2003AJ....125.2769S}.
\begin{itemize}
\item The simplest is the LQ case: this creates a saddle point and two
  minima in an arc, with the second saddle point on the other side of
  the lensing galaxy, closer to the galaxy than the arc.  \sw{58}
  and \sw{28} in the upper row of Fig.~\ref{fig:splinput} are typical
  examples of LQ.  If the source were moved outwards along the short
  axis, the minimum-saddle-minimum set would merge into a single minimum,
  leaving a D system; the transition is known as a cusp catastrophe.
\item The middle row of Fig.~\ref{fig:splinput} shows three IQ
  systems: \sw{05}, \sw{42} and \sw{19}.  This type has a characteristic
  asymmetry, often with two images close together.  If the source
  were moved outwards, the minimum-saddle pair would merge and
  mutually cancel, leaving again a D system. This transition is known
  as a fold catastrophe.
\item The lower row of Fig.~\ref{fig:splinput} shows three SQ
  systems: \sw{09}, \sw{29} and \sw{02}. The failed model, \sw{57}, at top right
  may also belong to this category.  Here the images have a
  fairly symmetric arrangement with an arc and a counter-image on the
  other side, but the spaghetti diagram is completely asymmetric.  If
  the source were moved outwards along the long axis, the
  saddle-minimum-saddle set  would merge into a single saddle --- another
  form of cusp catastrophe.  SQ can be visually distinguished from LQ
  by the relative distances of the arc and the counter-image.  For
  SQ the arc is closer, for LQ the counter-image is closer.
\end{itemize}
CQ systems are often called `cross' or `Einstein-cross' systems; IQ
systems are sometimes called `folds', with `cusp' commonly used for
both SQ and LQ.  The labels `short-axis quad' and so on are not
standard in the literature, but the morphological classification they
express is familiar to experienced modellers.  Hence they can be
useful to researchers wishing to apply other modelling methods to the
same systems.

>>>>

The main input of a modeller to the process is a markup of the
candidate lens system, which we call a spaghetti diagram.  This is a
sketch of the arrival-time surface from a point-like source, with
proposed locations of maxima, minima and saddle points, and an implied
time-ordering of the images.  Such information encodes a starting
proposal for the mass distribution.  A spaghetti diagram is thus a
completely abstract construction, and moreover it refers to a
simplified system with a point source.  However, spaghetti diagrams
are intuitive because they tend to resemble the form of lensed arcs
\citep[see Fig.~3 of][]{2008MNRAS.383..857F}, and of course they are
simple to draw, and easy to vary and refine in an open collaborative
environment. This makes them very practical for non-professional lens
enthusiasts in the citizen-science community.  Details and tests are
given in \citet{2015MNRAS.447.2170K}.

We now discuss the diagnostics that can be taken from the process of
drawing the spaghetti diagram, even before detailed mass-modelling
takes place.  Fig.~\ref{fig:splinput} shows nine examples, each
consisting of a cutout of the \SW  image of a lens candidate,
marked up with a spaghetti diagram.
The volunteers are initially presented a square image with side
\SI{82}{\arcsec} (\SI{440}{pixels}) in full size, but they have the
ability to zoom in individually.
The cutouts presented in Figs.~\ref{fig:splinput}--\ref{fig:kappa}
are rescaled during post-processing, relative to the outermost image.

@@

The third diagnostic tests whether the lens is isolated, or whether
other galaxies could contribute to the lensing, based on visual inspection 
of the field.
For this, we do not
consider stars or other clearly foreground objects.  Additional
galaxies contributing to the lensing mass can be marked by the
volunteer alongside the spaghetti diagrams.  An example can be seen as
the grey dot and circle in the cutout with \sw{57} at the top right of
Fig.~\ref{fig:splinput}.  Objects marked in this way are modelled as
point masses.  Other possible contributors to lensing are galaxies or
groups that are not in the immediate vicinity of the lensed images,
yet massive enough to exert an influence. These are accounted for by
allowing a constant but adjustable external shear.

We remark that the lack of expected lensed images, or the presence of
blended images or perturbing galaxies, does not imply that a given
candidate is unlikely to be a lens.  This means, rather, that the
models are more uncertain and perhaps could be more easily improved by
trying further variations in the markup.

The fourth diagnostic is based on the fact that the arrangement of
lensed images of a point-like source through a non-circular
gravitational lens depends on the location of the source relative to
the long and short axes of the lens.  This dependence is quite robust
and independent of many other details of the lensing mass
distribution.  Sources close to being dead-centre behind a lens tend
to produce quads; sources at larger transverse distance tend to
produce doubles.  We denote these as Q and D, respectively, and add a
prefix to the Q systems as follows: we write LQ if the source is
inferred as displaced along the long axis of the lens, SQ if displaced
along the short axis, IQ if inclined to both axes, and CQ if only very little or
no displacement is evident.  Although the
unlensed source and its location are obviously not seen, the LQ, SQ, IQ and CQ
cases correspond to easily seen image morphologies \citep[see,
  e.g.,][]{2003AJ....125.2769S}.

\begin{itemize}
\item The simplest is the LQ case: this creates a saddle point and two
  minima in an arc, with the second saddle point on the other side of
  the lensing galaxy, closer to the galaxy than the arc.  \sw{58}
  and \sw{28} in the upper row of Fig.~\ref{fig:splinput} are typical
  examples of LQ.  If the source were moved outwards along the short
  axis, the minimum-saddle-minimum set would merge into a single minimum,
  leaving a D system; the transition is known as a cusp catastrophe.
\item The middle row of Fig.~\ref{fig:splinput} shows three IQ
  systems: \sw{05}, \sw{42} and \sw{19}.  This type has a characteristic
  asymmetry, often with two images close together.  If the source
  were moved outwards, the minimum-saddle pair would merge and
  mutually cancel, leaving again a D system. This transition is known
  as a fold catastrophe.
\item The lower row of Fig.~\ref{fig:splinput} shows three SQ
  systems: \sw{09}, \sw{29} and \sw{02}. The failed model, \sw{57}, at top right
  may also belong to this category.  Here, the images have a
  fairly symmetric arrangement with an arc and a counter-image on the
  other side, but the spaghetti diagram is completely asymmetric.  If
  the source were moved outwards along the long axis, the
  saddle-minimum-saddle set  would merge into a single saddle -- another
  form of cusp catastrophe.  SQ can be visually distinguished from LQ
  by the relative distances of the arc and the counter-image.  For
  SQ, the arc is closer, and for LQ the counter-image is closer.
\end{itemize}
CQ systems are often called `cross' or `Einstein-cross' systems; IQ
systems are sometimes called `folds', with `cusp' commonly used for
both SQ and LQ.  The labels `short-axis quad' and so on are not
standard in the literature, but the morphological classification they
express is familiar to experienced modellers.  Hence, they can be
useful to researchers wishing to apply other modelling methods to the
same systems.

### 2017-12-04 parts/stelmass.tex
editors corrections

The stellar masses of the lens galaxies are derived by comparison of
the photometric data with stellar $M/L$ estimates from population
synthesis models.  In principle, a detailed analysis of the spectral
energy distribution is needed to derive accurate stellar masses
\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
at the redshifts probed, the photometric data mainly
constrain the information-rich 4000\thinspace\AA~break region, whose
strength depends sensitively on age and metallicity, thereby
providing a strong constraint on the stellar $M/L$.  Hence,
estimates to within $\sim$0.3\,dex in $\log(\Mstel/\Msun)$ can be derived
with a single colour, preferably tracing a rest-frame colour similar
to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}, assuming
a universal initial mass function (IMF).  There is
evidence from detailed absorption line strength analysis that massive
galaxies can feature a non-standard IMF 
\citep[e.g.][]{2013MNRAS.429L..15F}. However, these variations --
towards a bottom-heavy distribution -- are typically found in the
cores of massive early-type galaxies \citep{2016MNRAS.457.1468L}. The
effect of these variations on the stellar $M/L$ of lensing systems is
still rather controversial
\citep{2015MNRAS.449.3441S,2016MNRAS.459.3677L}.

In this paper we further simplify the analysis by assuming a
relationship between the apparent total magnitude and stellar mass, at
the redshift of the lens.  For typical stellar-population parameters,
the variation of this relation is at most $\Delta\log$M$_s\sim$1\,dex.
A further potential systematic can arise from contamination of the
light of the lensing galaxy by the lensed background source.  Reducing
or eliminating the latter would require detailed fitting of light
distributions for each candidate \citep[see][]{2011ApJ...740...97L},
which we have not yet attempted.  Nonetheless, because the lensing
masses range over two orders of magnitude, it is still interesting to
compare them with rough estimates of stellar mass.

We make use of the \citet{2003MNRAS.344.1000B} models to derive two
functional forms of the stellar mass with respect to the $i^{\prime}$-band
magnitudes. The models have solar metallicity, with a Chabrier IMF,
and assume two different age trends: a ``young'' model, with a
constant 500\,Myr age at all redshifts, and an ``old'' model where the
age is the oldest one possible at each redshift, adopting a standard
$\Lambda$CDM model with $H_0=70$\,km\,s$^{-1}$\,Mpc$^{-1}$ and
$\Omega_m=0.3$.

Fig.~\ref{fig:stelmass} shows a comparison of stellar and lensing mass
in our sample.  The comparatively large span of the error bars in
stellar mass (horizontal axis) shows the range between the masses
derived using the two age trends respectively, and lies between 0.4 and
0.8\,dex.  It will be improved in future work by the use of available
optical and NIR magnitudes to derive more accurate constraints on the
stellar populations.  In addition, we also derive halo masses for the
lenses using an abundance-matching formula.  This technique matches
the distribution function of observed stellar mass in galaxies with
that of dark-halo masses from $N$-body simulations, to define  a simple
relation between stellar mass and halo mass.  We emphasize that a halo
mass from abundance matching should be considered an ``average''
estimate, and a significant scatter can be expected as galaxies with
the same stellar mass can be found in different environments. We refer
the reader to \cite{2012MNRAS.424..104L} for an assessment of the
effect of abundance matching on the derivation of dark matter halo
properties in lensing galaxies. We follow the prescription of
\citet{2010ApJ...710..903M}, namely:
\begin{equation}
    \frac{\Mstel}{\Mhalo} = \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
                                     (\Mhalo/M_1)^\gamma}
\end{equation}
\begin{align*}
    C_0 &= 0.02820, & M_1 &= 10^{11.884} M_\odot \\
    \beta &= 1.057, & \gamma &= 0.556.
\end{align*}
Fig.~\ref{fig:stelmass} may be compared with Fig.~4 in
\cite{2011ApJ...734...69M}.
The comparison of lensing and stellar mass produces the last 
of our model diagnostics, defined as a halo-matching index:
\begin{equation}
\haloindex \equiv \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
\end{equation}
that relates the observed lensing to stellar mass, with the
global ratio expected if the host halo corresponds to the
average value derived by abundance matching. Several cases
for $\haloindex$ can be considered:
\begin{itemize}
\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
\item $\haloindex = 0$ means the stellar mass exactly accounts for the
  lensing mass (i.e. no dark matter affects the lensing model).
\item $0 < \haloindex < 1$ is the typical situation, where the lens
  includes stars and dark matter, but not the full halo.
\item $\haloindex = 1$ means that the lens consists of the entire halo.
\item $\haloindex > 1$ is in tension with abundance-matching, because the
  lensing mass exceeds the expected halo mass.
\end{itemize}
The halo-matching index expresses whether the lensing mass is
plausible given the flux received from the candidate lensing galaxy.

Fig.~\ref{fig:stelmass} and Table~\ref{tab:models} show that most of the
candidates have stellar
and lensing masses typical of massive ellipticals\footnote{The mass values
themselves are given in the online version of Table~\ref{tab:models}}.
\sw{05} is one of the most massive of all the candidates, corresponding
to a galaxy-group mass scale.  It is a particularly attractive system
for follow-up observations at higher resolution, as it is a large
system with clear multiple-image features. Modelling leaves little
doubt that it is a lens.  \sw{04} seems to be even more massive, but the
diagnostics leave some doubts about the validity of this model.  The
two lowest-mass systems, \sw{19} and \sw{42}, are important if they are
indeed lenses, as they would be low-mass lenses dominated by dark
matter.  All the modelled systems have reasonable stellar-mass
fractions, except for two cases where the stellar-mass fraction is too
low ($\haloindex > 1$): these are \sw{42} and \sw{57}.  In the case of \sw{57},
the model has poor diagnostics and should be discarded.  The model
for \sw{42}, on the other hand, is quite convincing -- except for the
high halo-matching index.  If \sw{42} turned out not to be a lens, that
would support the halo-matching index as an effective criterion to
discriminate models.

>>>>

The stellar masses of the lens galaxies are derived by a comparison of
the photometric data with stellar $M/L$ estimates from population
synthesis models.  In principle, a detailed analysis of the spectral
energy distribution is needed to derive accurate stellar masses
\citep[e.g.][]{2009ApJS..185..253G,2011MNRAS.418.1587T}.  However,
at the redshifts probed, the photometric data mainly
constrain the information-rich \SI{4000}{\angstrom} break region, whose
strength depends sensitively on age and metallicity, thereby
providing a strong constraint on the stellar $M/L$.  Hence,
estimates to within $\sim \SI{0.3}{dex}$ in $\log(\Mstel/\Msun)$ can be derived
with a single colour, preferably tracing a rest-frame colour similar
to $U-V$ \citep[see Fig.~1 of][]{2008MNRAS.383..857F}, assuming
a universal initial mass function (IMF).  There is
evidence from detailed absorption line strength analysis that massive
galaxies can feature a non-standard IMF 
\citep[e.g.][]{2013MNRAS.429L..15F}. However, these variations,
towards a bottom-heavy distribution, are typically found in the
cores of massive early-type galaxies \citep{2016MNRAS.457.1468L}. The
effect of these variations on the stellar $M/L$ of lensing systems is
still rather controversial
\citep{2015MNRAS.449.3441S,2016MNRAS.459.3677L}.

In this paper, we further simplify the analysis by assuming a
relationship between the apparent total magnitude and stellar mass, at
the redshift of the lens.  For typical stellar-population parameters,
the variation of this relation is at most
$\Delta \log \Mstel \sim \SI{1}{dex}$.
A further potential systematic can arise from contamination of the
light of the lensing galaxy by the lensed background source.  Reducing
or eliminating the latter would require detailed fitting of light
distributions for each candidate \citep[see][]{2011ApJ...740...97L},
which we have not yet attempted.  Nonetheless, because the lensing
masses range over two orders of magnitude, it is still interesting to
compare them with rough estimates of stellar mass.

We make use of the \citet{2003MNRAS.344.1000B} models to derive two
functional forms of the stellar mass with respect to the $i^{\prime}$-band
magnitudes. The models have solar metallicity, with a Chabrier IMF,
and assume two different age trends: a `young' model, with a
constant $\SI{500}{Myr}$ age at all redshifts, and an `old' model where the
age is the oldest one possible at each redshift, adopting a standard
$\Lambda$CDM model with $H_0 = \SI{70}{km.s^{-1}.Mpc^{-1}}$ and
$\Omega_m=0.3$.

Fig.~\ref{fig:stelmass} shows a comparison of stellar and lensing mass
in our sample.  The comparatively large span of the error bars in
stellar mass (horizontal axis) shows the range between the masses
derived using the two age trends, respectively, and lies between 0.4 and
\SI{0.8}{dex}.  It will be improved in future work by the use of available
optical and NIR magnitudes to derive more accurate constraints on the
stellar populations.  In addition, we also derive halo masses for the
lenses using an abundance-matching formula.  This technique matches
the distribution function of observed stellar mass in galaxies with
that of dark-halo masses from $N$-body simulations, to define  a simple
relation between stellar mass and halo mass.  We emphasize that a halo
mass from abundance matching should be considered an `average'
estimate, and a significant scatter can be expected as galaxies with
the same stellar mass can be found in different environments. We refer
the reader to \cite{2012MNRAS.424..104L} for an assessment of the
effect of abundance matching on the derivation of dark matter halo
properties in lensing galaxies. We follow the prescription of
\citet{2010ApJ...710..903M}, namely:
\begin{equation}
    \frac{\Mstel}{\Mhalo} = \frac{2C_0}{(\Mhalo/M_1)^{-\beta} +
                                     (\Mhalo/M_1)^\gamma}
\end{equation}
\begin{align*}
    C_0 &= 0.02820, & M_1 &= \SI{e11.884}{\Msun} \\
    \beta &= 1.057, & \gamma &= 0.556.
\end{align*}
Fig.~\ref{fig:stelmass} may be compared with Fig.~4 in
\cite{2011ApJ...734...69M}.
The comparison of lensing and stellar mass produces the last 
of our model diagnostics, defined as a halo-matching index:
\begin{equation}
\haloindex \equiv \frac{\ln(M/\Mstel)}{\ln(\Mhalo/\Mstel)}
\end{equation}
that relates the observed lensing to stellar mass, with the
global ratio expected if the host halo corresponds to the
average value derived by abundance matching. Several cases
for $\haloindex$ can be considered:
\begin{itemize}
\item $\haloindex < 0$ is unphysical because $M<\Mstel$.
\item $\haloindex = 0$ means the stellar mass exactly accounts for the
  lensing mass (i.e. no dark matter affects the lensing model).
\item $0 < \haloindex < 1$ is the typical situation, where the lens
  includes stars and dark matter, but not the full halo.
\item $\haloindex = 1$ means that the lens consists of the entire halo.
\item $\haloindex > 1$ is in tension with abundance matching, because the
  lensing mass exceeds the expected halo mass.
\end{itemize}
The halo-matching index expresses whether the lensing mass is
plausible given the flux received from the candidate lensing galaxy.

Fig.~\ref{fig:stelmass} and Table~\ref{tab:models} show that most of the
candidates have stellar
and lensing masses typical of massive ellipticals\footnote{The mass values
themselves are given in the online version of Table~\ref{tab:models}}.
\sw{05} is one of the most massive of all the candidates, corresponding
to a galaxy-group mass scale.  It is a particularly attractive system
for follow-up observations at higher resolution, as it is a large
system with clear multiple-image features. Modelling leaves little
doubt that it is a lens.  \sw{04} seems to be even more massive, but the
diagnostics leave some doubts about the validity of this model.  The
two lowest mass systems, \sw{19} and \sw{42}, are important if they are
indeed lenses, as they would be low-mass lenses dominated by dark
matter.  All the modelled systems have reasonable stellar-mass
fractions, except for two cases where the stellar-mass fraction is too
low ($\haloindex > 1$): these are \sw{42} and \sw{57}.  In the case of \sw{57},
the model has poor diagnostics and should be discarded.  The model
for \sw{42}, on the other hand, is quite convincing -- except for the
high halo-matching index.  If \sw{42} turned out not to be a lens, that
would support the halo-matching index as an effective criterion to
discriminate models.

### 2017-12-04 parts/summary.tex
working on letter2
editors corrections

We report on a first set of mass distributions and follow-up
diagnostics for the {\SW} lens candidates created with a novel
approach that aims to be scalable by {\sl orders of magnitude} to
prepare for the many thousands of lenses the next generation of wide
field surveys will yield (e.g. Euclid, WFIRST).

Over the past few years, the way of discovering lenses has changed
with the introduction of machine learning and citizen science methods,
combined with the coverage of large areas of the sky by modern
surveys.  The way lensing mass models are constructed also needs to
change, in order to be prepared for the increasing influx of lens
candidates.  The work in this paper represents a hybrid approach
between the classical style -- where a small team of experts invest
many hours into the creation of a single model -- and a citizen
science project -- where a crowd of amateur volunteers make
independent contributions.  The authors of this paper are a
collaboration of professionals and experienced citizen-science
volunteers, aiming to create early-stage lens models as soon as a lens
candidate is found.

To assist volunteers in constraining lensing models, we introduce a
set of diagnostics that help asses the validity of the models. At a
later stage, we encourage modellers to apply those diagnostics as
feedback on the plausibility of their assumptions, and to suggest
additional diagnostics.

The diagnostics (i) -- (iv) (see Section.~\ref{sec:candidates_models})
turned out to be useful measures of the difficulty in modelling a
system, but they did not constitute necessary conditions for a
promising model.  They can help select systems to introduce novice
volunteers to the modelling process. In contrast, diagnostics (v) and
(vi) can be considered as necessary criteria for a good model.
Volunteers employed those ones to evaluate their models, and turned out
to be easy enough to grasp by new volunteers.  The halo-matching
index diagnostic (vii, $\haloindex$), is an interesting criterion that
might be useful for the modellers, but needs further investigation.

Table~\ref{tab:models} is a summary of our results.  It characterises
each modelled system with seven diagnostics, indicating (a)~the image
morphology and how clear or indistinct it is, (b)~whether the mass map
and synthetic lensed image appear to be plausible, and (c)~how the
model mass compares with the estimated stellar and full-halo masses.
Missing entries are due unavailable imaging data, whereas 
missing rows are due to models that were not created for this particular
candidate.

The trend in Fig.~\ref{fig:stelmass}, where higher-mass galaxies get
progressively more dark-matter dominated, is expected
\citep[see, e.g.][]{2005ApJ...623L...5F}, as is the span of about one
order of magnitude for the stellar mass and the two orders of
magnitude in lensing mass. With future data, it will be interesting to
compare the enclosed stellar and lensing mass as a function of radius,
going from the star-dominated inner regions to the outer dark
halos. \citet{2011ApJ...740...97L} illustrate this behaviour in their
Fig.~5, but the present sample could go an order of magnitude higher
in mass.

The quick creation of many models for the {\SW} candidates
successfully showed that a subset of citizen scientists are interested
in being involved in more challenging tasks that take some time to
learn. The next step involves recruiting more lensing enthusiasts, as
soon as the next round of {\SW} is started. In the meantime, the
improvements shown in the Appendix will be integrated in the standard
version of {\SpL}. Photometric fitting could also be
integrated into {\SpL}. This would allow experienced citizen
scientists to generate photometric redshifts and stellar masses, and
thus generate preliminary dark-matter maps as soon as a lens-candidate
is identified.

>>>>

We report on a first set of mass distributions and follow-up
diagnostics for the {\SW} lens candidates created with a novel
approach that aims to be scalable by {\sl orders of magnitude} to
prepare for the many thousands of lenses the next generation of
wide-field surveys will yield (e.g. Euclid and WFIRST).

Over the past few years, the way of discovering lenses has changed
with the introduction of machine learning and citizen-science methods,
combined with the coverage of large areas of the sky by modern
surveys.  The way lensing mass models are constructed also needs to
change, in order to be prepared for the increasing influx of lens
candidates.  The work in this paper represents a hybrid approach
between the classical style, where a small team of experts invests
many hours into the creation of a single model, and a citizen-science
project, where a crowd of amateur volunteers makes
independent contributions.  The authors of this paper are a
collaboration of professionals and experienced citizen-science
volunteers, aiming to create early-stage lens models as soon as a lens
candidate is found.

To assist volunteers in constraining lensing models, we introduce a
set of diagnostics that helps us to assess the validity of the models. At a
later stage, we encourage modellers to apply those diagnostics as
feedback on the plausibility of their assumptions, and to suggest
additional diagnostics.

The diagnostics (i)--(iv) (see Section.~\ref{sec:candidates_models})
turned out to be useful measures of the difficulty in modelling a
system, but they did not constitute necessary conditions for a
promising model.  They can help select systems to introduce novice
volunteers to the modelling process. In contrast, diagnostics (v) and
(vi) can be considered as necessary criteria for a good model.
Volunteers employed those ones to evaluate their models, and turned out
to be easy enough to grasp by new volunteers.  The halo-matching
index diagnostic (vii, $\haloindex$) is an interesting criterion that
might be useful for the modellers, but needs further investigation.

Table~\ref{tab:models} is a summary of our results.  It characterizes
each modelled system with seven diagnostics, indicating (a)~the image
morphology and how clear or indistinct it is, (b)~whether the mass map
and synthetic lensed image appear to be plausible, and (c)~how the
model mass compares with the estimated stellar and full-halo masses.
Missing entries are due unavailable imaging data, whereas 
missing rows are due to models that were not created for this particular
candidate.

The trend in Fig.~\ref{fig:stelmass}, where higher-mass galaxies get
progressively more dark-matter dominated, is expected
\citep[see e.g.][]{2005ApJ...623L...5F}, as is the span of about one
order of magnitude for the stellar mass and the two orders of
magnitude in lensing mass. With future data, it will be interesting to
compare the enclosed stellar and lensing mass as a function of radius,
going from the star-dominated inner regions to the outer dark
haloes. \citet{2011ApJ...740...97L} illustrate this behaviour in their
fig.~5, but the present sample could go an order of magnitude higher
in mass.

The quick creation of many models for the {\SW} candidates
successfully showed that a subset of citizen-scientists is interested
in being involved in more challenging tasks that take some time to
learn. The next step involves recruiting more lensing enthusiasts, as
soon as the next round of {\SW} is started. In the meantime, the
improvements shown in the appendix will be integrated in the standard
version of {\SpL}. Photometric fitting could also be
integrated into {\SpL}. This would allow experienced citizen
scientists to generate photometric redshifts and stellar masses, and
thus generate preliminary dark-matter maps as soon as a lens candidate
is identified.

\section{Acknowledgements}\label{sec:ack}
This work was supported by the University of Zurich
Candoc reseach grant (Forschungskredit Candoc; FK-14-
081 and FK-15-087).
